\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{parskip}

% --- Colors ---
\definecolor{primary}{RGB}{35, 55, 123}
\hypersetup{colorlinks=true, urlcolor=primary}

\begin{document}

% --- SENDER ---
\noindent
\begin{minipage}[t]{0.5\textwidth}
    \textbf{Loic Aron MBASSI EWOLO}\\
    Engineering Student (Bac+5) -- Double Degree ENSEA/Polytechnique\\[3pt]
    \Mobilefone\ (+33) 7 59 52 33 98\\
    \Letter\ \href{mailto:loicaron.mbassiewolo@ensea.fr}{loicaron.mbassiewolo@ensea.fr}
\end{minipage}
\hfill
% --- DATE ---
\begin{minipage}[t]{0.4\textwidth}
    \raggedleft
    Cergy, March 21, 2026
\end{minipage}

\vspace{1.2cm}

% --- RECIPIENT ---
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{MobSuccess} \\
    Recruitment Team \\
    Paris, France
\end{minipage}

\vspace{1cm}

\noindent\textbf{Subject:} Application for Data Engineer Internship (Paris)

\vspace{0.8cm}

Dear Sir or Madam,

ETL pipelines, SQL optimization, and distributed data systems are the core of my engineering practice. Currently at INRIA Saclay, I built large-scale data processing pipelines handling 10k+ mobile app datasets: extracting heterogeneous data sources, standardizing formats, validating quality, and feeding ML models. This hands-on experience at France's top computer science institute demonstrates my commitment to scalable, production-grade data engineering.

My data engineering track record spans multiple sectors: I designed PostgreSQL schemas with composite indexing supporting 1000+ QPS messaging traffic (Snappy platform); maintained MySQL telemedicine databases over 2+ years of production operation (SOSDOCTA), optimizing query performance and executing zero-downtime migrations; implemented fintech transaction audit trails with precise financial reconciliation (CSC); and orchestrated asynchronous data flows across microservices using RabbitMQ and MongoDB. I am proficient in SQL optimization, Python data processing (pandas, NumPy), Redis caching architectures, and CI/CD deployment practices.

MobSuccess's adtech data scale and real-time analytics requirements align with my backend and data systems expertise. I am available for a 12-month alternance starting September 2026, and I am excited to apply my data infrastructure knowledge to accelerate your Paris engineering team's growth.

I welcome the opportunity to discuss how my SQL expertise, ETL design skills, and production engineering experience can strengthen MobSuccess's data platform.

Yours faithfully,

\vspace{0.8cm}

\textbf{Loic Aron MBASSI EWOLO}\\
\textit{Engineering Student, ENSEA / Polytechnique Yaounde}

\end{document}
