\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{parskip}

% --- Colors ---
\definecolor{primary}{RGB}{0, 45, 114}
\hypersetup{colorlinks=true, urlcolor=primary}

\begin{document}

% --- SENDER ---
\noindent
\begin{minipage}[t]{0.5\textwidth}
    \textbf{Loic Aron MBASSI EWOLO}\\
    Engineering Student (Bac+5) -- Double Degree ENSEA/Polytechnique\\[3pt]
    \Mobilefone\ (+33) 7 59 52 33 98\\
    \Letter\ \href{mailto:loicaron.mbassiewolo@ensea.fr}{loicaron.mbassiewolo@ensea.fr}
\end{minipage}
\hfill
% --- DATE ---
\begin{minipage}[t]{0.4\textwidth}
    \raggedleft
    Cergy, March 21, 2026
\end{minipage}

\vspace{1.2cm}

% --- RECIPIENT ---
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Thales} \\
    Recruitment Team \\
    Toulouse, France
\end{minipage}

\vspace{1cm}

\noindent\textbf{Subject:} Application for AI Engineer Internship (Toulouse)

\vspace{0.8cm}

Dear Sir or Madam,

Transformers, NLP pipelines, and neural network interpretability are the focus of my applied research. Currently at INRIA Saclay (TRIBE team), I built large-scale NLP analysis systems using BERT to evaluate privacy compliance in 10k+ mobile app policies, synthesizing model outputs into a trust score for end-users and security teams. This hands-on work at France's top AI research institute demonstrates both my technical depth and commitment to production-grade machine learning.

Beyond INRIA, my AI portfolio spans defense-relevant domains: I conducted grokking research at MILA (OpenAI phenomenon on generalization), developed CNN classifiers for medical imaging (92\% ECG anomaly detection), fine-tuned BERT to detect misogyny in job postings (Women Safe competition), and orchestrated multi-agent LLM systems with RAG for knowledge retrieval. I am proficient in PyTorch, TensorFlow, Hugging Face Transformers, Docker, and Git -- proven through open-source contributions and 50+ research presentations.

Thales Toulouse's focus on advanced AI for defense applications aligns with my research orientation and technical ambitions. I am available for a 12-month alternance starting September 2026, and I am excited to apply my deep learning expertise and research rigor to your Toulouse teams.

I welcome discussing how my NLP, computer vision, and interpretability background can contribute to your defense AI initiatives.

Yours faithfully,

\vspace{0.8cm}

\textbf{Loic Aron MBASSI EWOLO}\\
\textit{Engineering Student, ENSEA / Polytechnique Yaounde}

\end{document}
