\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{parskip}

% --- Colors ---
\definecolor{primary}{RGB}{0, 45, 114}
\hypersetup{colorlinks=true, urlcolor=primary}

\begin{document}

% --- SENDER ---
\noindent
\begin{minipage}[t]{0.5\textwidth}
    \textbf{Loic Aron MBASSI EWOLO}\\
    Engineering Student (Bac+5) -- Double Degree ENSEA/Polytechnique\\[3pt]
    \Mobilefone\ (+33) 7 59 52 33 98\\
    \Letter\ \href{mailto:loicaron.mbassiewolo@ensea.fr}{loicaron.mbassiewolo@ensea.fr}
\end{minipage}
\hfill
% --- DATE ---
\begin{minipage}[t]{0.4\textwidth}
    \raggedleft
    Cergy, March 21, 2026
\end{minipage}

\vspace{1.2cm}

% --- RECIPIENT ---
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Thales} \\
    Recruitment Team \\
    Elancourt, France
\end{minipage}

\vspace{1cm}

\noindent\textbf{Subject:} Application for Signal Processing and AI Engineer Internship (Elancourt)

\vspace{0.8cm}

Dear Sir or Madam,

Sensor fusion, signal conditioning, and real-time anomaly detection are my core technical interests. Currently completing a research internship at INRIA Saclay (TRIBE team, privacy-preserving data science), I am applying for the Signal Processing and AI engineer position at Thales Elancourt because your defense AI applications align perfectly with my embedded ML and signal analysis background.

My INRIA stage involved designing automated analysis pipelines for mobile app security: I built large-scale NLP and signal processing workflows to detect privacy leaks, modeling permission requests as time-series anomalies and applying BERT-based classifiers to detect non-transparent data access patterns. This hands-on experience with Python, PyTorch, and numerical analysis at scale gives me confidence in tackling signal processing challenges in defense contexts.

Beyond INRIA, I have deployed signal-based ML systems in hardware: designing STM32 firmware for IMU and flex sensor fusion on Harmony Gloves (complementary filtering, real-time feature extraction), optimizing CNN models for ECG anomaly detection (92\% accuracy on arrhythmia classification), and integrating YOLO and Lidar point-cloud processing on Nvidia Jetson (SLAM pipeline, 3D object detection). I am fluent in MATLAB/Simulink (fault detection modeling, control systems), TensorFlow, and embedded C/C++.

I am available for a 12-month alternance starting September 2026 following my INRIA stage. My technical depth in sensor signal processing, embedded ML optimization, and defense-relevant applications makes me ready to contribute immediately to your Elancourt teams.

I welcome the opportunity to discuss how my signal processing expertise and research rigor can accelerate Thales' AI defense initiatives.

Yours faithfully,

\vspace{0.8cm}

\textbf{Loic Aron MBASSI EWOLO}\\
\textit{Engineering Student, ENSEA / Polytechnique Yaounde}

\end{document}
