\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{parskip}

% --- Colors ---
\definecolor{primary}{RGB}{0, 122, 195}
\hypersetup{colorlinks=true, urlcolor=primary}

\begin{document}

% --- SENDER ---
\noindent
\begin{minipage}[t]{0.5\textwidth}
    \textbf{Loic Aron MBASSI EWOLO}\\
    Engineering Student (Bac+5) -- Double Degree ENSEA/Polytechnique\\[3pt]
    \Mobilefone\ (+33) 7 59 52 33 98\\
    \Letter\ \href{mailto:loicaron.mbassiewolo@ensea.fr}{loicaron.mbassiewolo@ensea.fr}
\end{minipage}
\hfill
% --- DATE ---
\begin{minipage}[t]{0.4\textwidth}
    \raggedleft
    Cergy, March 21, 2026
\end{minipage}

\vspace{1.2cm}

% --- RECIPIENT ---
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \textbf{Capgemini} \\
    Recruitment Team \\
    Toulouse, France
\end{minipage}

\vspace{1cm}

\noindent\textbf{Subject:} Application for Cybersecurity Engineer Internship (Toulouse)

\vspace{0.8cm}

Dear Sir or Madam,

Cryptography, privacy architecture, and threat modeling are my core security competencies. Currently at INRIA Saclay, I built privacy assessment frameworks analyzing 10k+ mobile applications for RGPD compliance, combining NLP-based policy analysis with static code inspection to detect privacy violations and non-transparent data collection. This hands-on research at France's leading computer science institute demonstrates my commitment to rigorous, defense-grade security practices.

My cybersecurity portfolio spans cryptographic implementation and secure architecture: I designed end-to-end encrypted messaging (Snappy platform) implementing the Signal Protocol with Perfect Forward Secrecy and AES-256-GCM hybrid encryption; secured fintech payment systems (CSC) with transaction auditing and compliance logging; maintained SOSDOCTA's HIPAA-equivalent medical data protection across two years of production; and applied POSIX IPC security principles in multi-process systems. I am proficient in cryptographic primitives, secure development lifecycle, RGPD compliance assessment, and DevSecOps practices.

Capgemini's cybersecurity consulting mission in Toulouse aligns with my security research orientation and aspirations to protect critical systems. I am available for a 12-month alternance starting September 2026, and I am prepared to contribute immediately to your security architecture and consulting teams.

I welcome the opportunity to discuss how my cryptography expertise, privacy knowledge, and secure development practices can strengthen Capgemini's defense and enterprise security offerings.

Yours faithfully,

\vspace{0.8cm}

\textbf{Loic Aron MBASSI EWOLO}\\
\textit{Engineering Student, ENSEA / Polytechnique Yaounde}

\end{document}
